Renewal and stability in populations structured by remaining years of life

### 2014-09-03 ThanoRepro/ThanoRepro.tex
changed integrand to t

\section{Equivalence in stability}
\label{app:B}
This appendix contains a proof that the thanatological renewal equation implies
the same intrinsic growth rate, $r$, as Lotka's chronological renewal model if
the starting population is stable. This is identical to claiming that the right
side of the rewal equation is equal given the same $r$. Since there is a unique
real solution, demonstrated in the previous appendix, then it is sufficient to
show that the two integral equations are equal under these conditions. The basic
relationship is:
\begin{align}
\int _{a=0}^\infty l(a)e^{-ra}f(a) \dd a &= \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra}f^\star (y) \dd a \dd y
\intertext{when}
f^\star(y) &= \frac{b^\star(y)}{c^\star(y)} \\
b^\star (y) &= \int_{a=0}^\infty b(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a \\
c^\star (y) &= \int_{a=0}^\infty c(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a
\intertext{Note that:}
c(a) &= \frac{l(a)r^{-ra}}{\int l(a) e^{-ra} \dd a} \\
b(a) &= f(a)c(a)
\end{align}
Replacing $f^\star (y)$ with the full expanded expression and
plugging into the thanatological renewal equation gives:
\begin{align}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{\frac{\int_{a=0}^\infty
f(a)l(a)e^{-ra}\mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{\int l(a) e^{-ra} \dd
a}}{\frac{\int_{a=0}^\infty l(a)e^{-ra} \mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{\int l(a) e^{-ra} \dd a}} \dd a \dd y
\intertext{The denominator of $c(a)$ cancels out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{a=0}^\infty
f(a)l(a)e^{-ra}\mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{
\int_{a=0}^\infty l(a)e^{-ra} \mu(a+y)\frac{l(a+y)}{l(a)} \dd a} \dd a \dd y
\intertext{Some $l(a)$'s also cancel out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{a=0}^\infty
f(a)e^{-ra}\mu(a+y)l(a+y) \dd a}{
\int_{a=0}^\infty e^{-ra} \mu(a+y)l(a+y) \dd a} \dd a \dd y
\intertext{Now $d(a+y) = \mu (a+y)l(a+y)$, so we can cancel the inner integral
with the denominator:}
=& \int _{y=0}^\infty 
\int_{a=0}^\infty
f(a)e^{-ra}\mu(a+y)l(a+y) \dd a \dd y
\intertext{Note also that $l(a) = \int _{x=a}^\infty d(x) \dd x$ (present
livings are future deaths), which brings us back to the chronological
formulation:} =& \int_{a=0}^\infty e^{-ra}l(a)f(a)
\dd a
\end{align}
\end{appendices}
\nocite{HMD,HFD}
% --------------------------------------------------
% bibliography
\bibliographystyle{plainnat}
  \bibliography{References}

>>>>

\section{Equivalence in stability}
\label{app:B}
This appendix contains a proof that the thanatological renewal equation implies
the same intrinsic growth rate, $r$, as Lotka's chronological renewal model if
the starting population is stable. This is identical to claiming that the right
side of the rewal equation is equal given the same $r$. Since there is a unique
real solution, demonstrated in the previous appendix, then it is sufficient to
show that the two integral equations are equal under these conditions. The basic
relationship is:
\begin{align}
\int _{a=0}^\infty l(a)e^{-ra}f(a) \dd a &= \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra}f^\star (y) \dd a \dd y
\intertext{when}
f^\star(y) &= \frac{b^\star(y)}{c^\star(y)} \\
b^\star (y) &= \int_{a=0}^\infty b(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a \\
c^\star (y) &= \int_{a=0}^\infty c(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a
\intertext{Note that:}
c(a) &= \frac{l(a)r^{-ra}}{\int l(a) e^{-ra} \dd a} \\
b(a) &= f(a)c(a)
\end{align}
Replacing
$f^\star (y)$ with the full expanded expression and plugging into the thanatological renewal equation gives:
\begin{align}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{\frac{\int_{t=0}^\infty
f(t)l(t)e^{-rt}\mu(a+y)\frac{l(t+y)}{l(t)} \dd t}{\int l(t) e^{-rt} \dd
t}}{\frac{\int_{t=0}^\infty l(t)e^{-rt} \mu(t+y)\frac{l(t+y)}{l(t)} \dd t}{\int
l(t) e^{-rt} \dd t}} \dd a \dd y
\intertext{The denominator of $c(a)$ cancels out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{t=0}^\infty
f(t)l(t)e^{-rt}\mu(t+y)\frac{l(t+y)}{l(t)} \dd t}{
\int_{t=0}^\infty l(t)e^{-rt} \mu(t+y)\frac{l(t+y)}{l(t)} \dd t} \dd a \dd y
\intertext{Some $l(a)$'s also cancel out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{t=0}^\infty
f(t)e^{-rt}\mu(t+y)l(t+y) \dd t}{
\int_{t=0}^\infty e^{-rt} \mu(t+y)l(t+y) \dd t} \dd a \dd y
\intertext{Now $d(a+y) = \mu (a+y)l(a+y)$, so we can cancel the inner integral
with the denominator:}
=& \int _{y=0}^\infty 
\int_{a=0}^\infty
f(a)e^{-ra}\mu(a+y)l(a+y) \dd a \dd y
\intertext{Note also that $l(a) = \int _{x=a}^\infty d(x) \dd x$ (present
livings are future deaths), which brings us back to the chronological
formulation:} =& \int_{a=0}^\infty e^{-ra}l(a)f(a)
\dd a
\end{align}
\end{appendices}
\nocite{HMD,HFD}
% --------------------------------------------------
% bibliography
\bibliographystyle{plainnat}
  \bibliography{References}
